\documentclass[helvetica,narrow,openbib,notitle,flagCMYK]{europecv}
\usepackage[T1]{fontenc}
\usepackage[a4paper,top=1.27cm,left=1cm,right=1cm,bottom=2cm]{geometry}
\usepackage{ifpdf}
\usepackage{bibentry}
\usepackage[english]{babel}
\ifpdf
    \usepackage[pdftex]{graphicx}
\else
     \usepackage{graphicx}
\fi

\renewcommand{\ttdefault}{phv}

\ecvname{Proverbio, Michele}
\ecvfootername{Michele Proverbio}
\ecvaddress{Via Anita Garibaldi 8, Cesena(FC)}
\ecvtelephone[3393101652]{0717922826}
\ecvnationality{Italian}
\ecvdateofbirth{November 15, 1992}
\ecvemail{proch92@gmail.com}


\begin{document}
	\begin{europecv}
	\ecvpersonalinfo[20pt]

	\ecvsection{Spoken Languages}

	\ecvmothertongue[10pt]{Italian}
	\ecvlanguageheader{(*)}
	\ecvlanguage{English}{\ecvBTwo}{\ecvBTwo}{\ecvBTwo}{\ecvBTwo}{\ecvBTwo}
	\ecvlanguagefooter{(*)}

	\ecvsection{Education}
	\ecvitem{October 2014 - Now} {
				Master Degree in Computer Science and Engineer in Cesena.

				Major academic courses highlight: DataWarehouse & Business intelligence, Machine Learning, Advanced programming.}
	\ecvitem{October 2011 - March 2015}{
				Computer Science in Cesena, University of Bologna.

				Graduated with 100/110.

				Thesis argument: Security of authentication systems. Gathering and analysis of a wide collection of real password.

				Major academic courses highlight: Computer networks, Software engineering, High Performance Computing, Mobile web design.}
	\ecvitem{2006 - 2011}{Science and Math High School at ``Liceo scientifico Enrico Medi'' in Senigallia}

	\ecvsection{Occupation}
	\ecvitem{April 2015 - December 2018} {
			System administrator and Machine Learning consultant at Onit Group srl.

			Linux and Windows server administration. Active Directory. VMware virtual environment.

			Apache Spark. HP Vertica.
	}
	\ecvitem{Dicember 2013 - March 2014} {
			Teacher at ``Linux Ubuntu and Trashware'' courses in Ostra and Corinaldo.

			Held by Informagiovani Senigallia.
	}
	\ecvitem{2012-2015} {
			IT technical customer assistance. Internet and LAN configurations. Basic computer courses.
	}

	\ecvsection{Competencies \& Interests}
	\ecvitem{Technical skills} {
		\begin{itemize}
			\item I am proficient in both Linux and Windows operative systems.
			\item I am proficient in C, C++11 and Python 2/3, and i have developed good experience with Ruby, JS and Java.
			\item I have experience with all programming paradigms: Imperative, OOP, functional, logic, Constraint.
			\item Technologies i have experience with:
			\item OpenMP, OpenMPI, OpenCL, CUDA, OpenGL, GL/SL, Vulkan.
			\item Version Control: git, base understanding of mercurial.
			\item Web development: HTML5, CSS3, Javascript, Typescript, Angular, Python, Django, Jinja2, Middleman.
			\item Mobile development: Android, WP 8.1, base understanding of IOS system.
			\item I have very good understandings of Unix-like systems; i can use the shell and make shell scripts.
			\item Development Environments: Vim, Eclipse, NetBeans, GNU compilers, and base knowledge of Microsoft Visual Studio and .NET environment.
		\end{itemize}
	}
	\ecvitem[10pt]{Interests and events} {
		\begin{itemize}
			\item I am interested in GNU/Linux ecosystem, computer security, videogame development and Artificial Intelligence. 
			\item I have attended a national competition in Turin on Robotics in the Rescue category (RoboCup Jr 2009) 
			\item I am taking part in a computer security group in Cesena (CeSeNA), and i attended a few CTF and Wargames like ruCTF, DEFCON qualifiers, CSAW, iCTF etc.
			\item I took part in several Hackaton on Artificial Intelligence and Machine Learning
		\end{itemize}
	}
	\ecvitem[10pt]{Sports} {Basketball, Waterpolo, Rugby}


	\end{europecv}
\end{document}
